### 2019-02-15 README.Rmd
Author names

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>% 
  purrr::keep(~"aut" %in% .$role) %>% 
  purrr::map_chr(~paste(.$given, .$family)) %>% 
  paste(collapse = ", ") %>% 
  paste0("Authors: _", ., "_") %>% 
  cat()
```

@@

```{r version}
packageVersion("citesdb")
```

>>>>

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>% 
  purrr::keep(~"aut" %in% .$role) %>% 
  purrr::map_chr(~paste(.$given, .$family)) %>% 
  glue::glue_collapse(sep = ", ", last = ", and ") %>% 
  paste0("Authors: _", ., "_") %>% 
  cat()
```

@@

```{r version}
#packageVersion("citesdb")
```
